---
title: "GSE85718"
output: 
  html_document:
    toc: true
    toc_float:
      collapse: false
      smooth_scroll: false
runtime: shiny
---

<style>
table {
  white-space: nowrap;
}
.datatables {
  overflow: auto;
}

hr {
  border-top: solid 1px black;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
pkgs = c("dplyr", "reshape2", "glue", "ggplot2", "Biobase", "DT", "plotly")
for(pkg in pkgs) library(pkg, character.only = TRUE)
```

```{r}
load("../../GSE85718.rda")
```

## 1. Glycosyltransferase

I search on PubMed database, with the keywords **(glycosyltransferases) AND "Mus musculus"**, and downloaded 39 records. Click on the row to see the boxplot.

```{r}
glycotrans_list = read.table("../../glycotransferase_gene_list.txt", sep = "\t", header = TRUE, stringsAsFactors = FALSE)
datatable(glycotrans_list)
```

I cross searched those **39** genes in this dataset, and found 10 matches. Below is the feature information data of them.

```{r}
gs = which(fData(gset)$Symbol %in% glycotrans_list$Symbol)

fdata_sub = fData(gset)[gs,]
output$glyco = renderDataTable(
  fdata_sub,
  selection = list(mode = "single", selected = 1),
  server=T
)
dataTableOutput("glyco")
```

```{r}
makeBoxPlot = function(i){
    data.frame(
        value = exprs(gset)[i,],
        source = pData(gset)$source_name_ch1
    ) %>%
        ggplot(aes(x = source, y =value)) +
        geom_boxplot() +
        theme_bw() +
        theme(
            axis.text.x = element_text(angle = 45, hjust = 1),
            plot.title = element_text(hjust = 0.5)
        )
}
renderPlotly({
  i = input$glyco_rows_selected
  makeBoxPlot(gs[i]) + labs(title = fdata_sub$Symbol[i])
})
```

<hr />

## 2. ABCA1

```{r}
(makeBoxPlot(which(fData(gset)$Symbol == "Abca1")) + 
  labs(title = "ABCA1")) %>% 
  ggplotly
```

<hr />

## 3. ApoA1

```{r}
(makeBoxPlot(which(fData(gset)$Symbol == "Apoa1")) + 
  labs(title = "Apoa1")) %>% 
  ggplotly
```

<hr />

## 4. GALNT

I searched all GALNT in the dataset, and found **26** matches. They all seems to be members of the GALNT gene family. Again, click to see the boxplot

```{r}
gs2 = grep("galnt", tolower(fData(gset)$Symbol))

fdata_sub2 = fData(gset)[gs2,]
output$galnt = renderDT(
  fdata_sub2,
  selection = list(mode = "single", selected = 1),
  server=T
)
DTOutput("galnt")
```

```{r}
renderPlotly({
  i = input$galnt_rows_selected
  makeBoxPlot(gs2[i]) + labs(title = fdata_sub2$Symbol[i])
})
```

<hr />

## 4. St3Gal

There is no St3Gal1 or St3Gal2 in the data, but I found St3Gal3 and 4.

```{r}
gs3 = grep("st3gal", tolower(fData(gset)$Symbol))

fdata_sub3 = fData(gset)[gs3,]
output$st3gal = renderDT(
  fdata_sub3,
  selection = list(mode = "single", selected = 1),
  server=T
)
DTOutput("st3gal")
```

```{r}
renderPlotly({
  i = input$st3gal_rows_selected
  makeBoxPlot(gs3[i]) + labs(title = fdata_sub3$Symbol[i])
})
```

<hr />

## 6. ST6GalNAc

```{r}
gs4 = grep("st6galnac", tolower(fData(gset)$Symbol))

fdata_sub4 = fData(gset)[gs4,]
output$st6galnac = renderDT(
  fdata_sub4,
  selection = list(mode = "single", selected = 1),
  server=T
)
DTOutput("st6galnac")
```

```{r}
renderPlotly({
  i = input$st6galnac_rows_selected
  makeBoxPlot(gs4[i]) + labs(title = fdata_sub4$Symbol[i])
})
```

<hr />

## 7. FUT

```{r}
gs5 = grep("fut", tolower(fData(gset)$Symbol))

fdata_sub5 = fData(gset)[gs5,]
output$fut = renderDT(
  fdata_sub5,
  selection = list(mode = "single", selected = 1),
  server=T
)
DTOutput("fut")
```

```{r}
renderPlotly({
  i = input$fut_rows_selected
  makeBoxPlot(gs5[i]) + labs(title = fdata_sub5$Symbol[i])
})
```