---
title: "GSE85718"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r}
library(Biobase); library(GEOquery)
```

## Get GSE85718 data

```{r}
gset <- getGEO("GSE85718", GSEMatrix =TRUE, getGPL=TRUE)
gset = gset[[1]]
save(gset, file = "../GSE85718.rda")
```

Below shows that the GSE85718 has 25697 features and 8 samples

```{r}
gset
```

The sample meta-data has 40 variables. Below is the first 6 rows (samples).

```{r}
head(pData(gset))
```

The study design information seems to be stored in the `source_name_ch1` column. There are 12 treatment/groups, and 4 samples in each treatment.

```{r}
table(pData(gset)$source_name_ch1)
```

The feature data has 28 columns/variables. Below is the first 6 rows. The `Symbol` column is the common abbreviate. The `Definition` column has more information about this transcript.

```{r}
head(fData(gset))
```

## Glycosyltransferase

I search on PubMed database, with the keywords **(glycosyltransferases) AND "Mus musculus"**, and downloaded 39 records.

```{r}
glycotrans_list = read.table("../glycotransferase_gene_list.txt", sep = "\t", header = TRUE, stringsAsFactors = FALSE)
glycotrans_list
```

I cross searched those 39 genes in this dataset, and found 10 matches. Below is the feature information data of them.

```{r}
gs = which(fData(gset)$Symbol %in% glycotrans_list$Symbol)
fData(gset)[gs,]
```

Then for each individual feature, I made a boxplot, with treatment/group (the `source_name_ch1` column) in the x axis.

```{r}
library(ggplot2); library(dplyr)
makeBoxPlot = function(i){
    gene_name = glycotrans_list$description[which(glycotrans_list$Symbol == fData(gset)$Symbol[i])]
    data.frame(
        value = exprs(gset)[i,],
        source = pData(gset)$source_name_ch1
    ) %>%
        ggplot(aes(x = source, y =value)) +
        geom_boxplot() +
        labs(title = gene_name) +
        theme_bw() +
        theme(
            axis.text.x = element_text(angle = 45, hjust = 1),
            plot.title = element_text(hjust = 0.5)
        )
}
makeBoxPlot(gs[1])
```

```{r}
makeBoxPlot(gs[2])
```

```{r}
makeBoxPlot(gs[3])
```

```{r}
makeBoxPlot(gs[4])
```

```{r}
makeBoxPlot(gs[5])
```

```{r}
makeBoxPlot(gs[6])
```

```{r}
makeBoxPlot(gs[7])
```

```{r}
makeBoxPlot(gs[8])
```

```{r}
makeBoxPlot(gs[9])
```


```{r}
makeBoxPlot(gs[10])
```


## ABCA1

```{r}
gs = which(fData(gset)$Symbol == "Abca1")
makeBoxPlot = function(i){
    data.frame(
        value = exprs(gset)[i,],
        source = pData(gset)$source_name_ch1
    ) %>%
        ggplot(aes(x = source, y =value)) +
        geom_boxplot() +
        theme_bw() +
        theme(
            axis.text.x = element_text(angle = 45, hjust = 1),
            plot.title = element_text(hjust = 0.5)
        )
}
makeBoxPlot(gs) + labs(title = "ABCA1")
```

## ApoA1

```{r}
gs = which(fData(gset)$Symbol == "Apoa1")
makeBoxPlot(gs) + labs(title = "ApoA1")
```

## GALNT2

There are three **GALNT2** in this dataset.

```{r}
gs = which(fData(gset)$Symbol == "Galnt2")
fData(gset)[gs,]
```

```{r}
makeBoxPlot(gs[1])
```

```{r}
makeBoxPlot(gs[2])
```

```{r}
makeBoxPlot(gs[3])
```

